---
title: "SNP-Chip Data Analysis with Plink and R"
author: "Bernice Waweru"
date: "`r format(Sys.time(), '%a %d, %b %Y')`"
output:
  github_document:
    toc: true
    fig_width: 12
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Objective and info on data 

To analyse goat diversity with data generated through goat genome SNP Chip from illumina through labogena. The goatiggc_cons_60k SNPChip includes 53,347 SNPS typed on the samples 
Data on the hpc found here (/home/bngina/Fellows/goat_diversity/orig_data/oct_2019)
Original file has 648 samples, as calculated from the ped file (less -S orig_data/oct_2019/Caprin_60k.ped | wc -l)


## load required tools 

module load plink/1.9


# ===== define path variables =======================================

# ===== file prefix of the map and ped file 

file='/home/bngina/Fellows/goat_diversity/orig_data/oct_2019/Caprin_60k'

#===== dir to store the output files generated during analysis ======

out='/home/bngina/Fellows/goat_diversity/plink_out_march_2021'


### Session Info

Details of packages used with the work flow

```{r}
devtools::session_info()
```

